---
title: "Swiftkey Text Prediction Application"
author: "Ariful Mondal"
date: "29 December 2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is a sample shiny app to predict text which is a data science capstone project from ["Data Science Specialization"](https://www.coursera.org/specializations/jhu-data-science) Learning path on [Coursera](https://www.coursera.org) by [Johns Hopkins University](https://www.jhu.edu/). 

This project is supported by [SwiftKey](https://swiftkey.com/en), corporate partner in this capstone, builds a smart keyboard that makes it easier for people to type on their mobile devices.

## Interactive Plot

```{r eruptions}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## R Output

```{r cars}
summary(cars)
```


